Low Complexity Adaptive Sonar Imaging

### 2016-03-02 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2016:03:01	20:27:55	(ti. 1.mars)
la2pdf commit - 2016:03:02	09:22:10	(on. 2.mars)

\IEEEPARstart{T}{he} best sonars in existence is perhaps found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. No man made sonar can currenly match this feat, much due to the challenge of processing and adapting to a complex environment fast enough. While human made sonars have little to no adaptivity on transmit, several methods have been investigated to adaptively post process the received data. Perhaps the best studied method for reconstructing a sonar image is the minimum variance distortion-less response (MVDR) beamformer~\cite{Capon1969}. It adapts the sonar array's spatial response to minimize the influence of noise and interference in the final image.

@@

% \section{Steering angle}

@@

% \section{Multimedia Files and Source Code}\label{source_code}

>>>>

\IEEEPARstart{T}{he} best sonars in existence is perhaps found in nature. Bats, for instance, use a high frequency sonar to detect, identify and track prey with amazing precision in caves amongst a myriad of other bats. No man made sonar can currenly match this feat, much due to the challenge of processing and adapting to such a complex environment fast enough. This is why human made sonars have little to no adaptivity on transmit. On the receiving side, however, several methods have been investigated to adaptively post process the received data. Perhaps the most well known method for reconstructing a sonar image out of the data is the minimum variance distortion-less response (MVDR) beamformer~\cite{Capon1969}. It adapts the sonar array's spatial response to minimize the influence of noise and interference in the final image.

@@

\section{Steering angle}

@@

\section{Multimedia Files and Source Code}\label{source_code}

### 2016-03-02 LCAforActiveSonarImaging/submission/submit1/answer/answer.tex
la2pdf commit - 2016:03:02	09:22:10	(on. 2.mars)

\begin{enumerate}
% \emph{General}
\hi{Introduction}
\qi{The authors show no evidence that bats use adaptive processing, remove this example.}
\ai{The reviewer makes a good point, this may not have been obvious. We have provided a reference for the adaptive processing used by bats, but would prefer to keep the example if possible.}
%
\qi{It is not clear whether LCA is really an adaptive method that adapts weights on the fly or a method that a posteriori decides which window shows best results.}
\ai{We appreciate the remark. We are using a system level definition of adaptivity that includes any kind of dynamic and data dependent behaviour, hence feel that both beamformers fall in that category. Both methods process the pixels in a data dependent manner, resulting in non linear image. We have tried to express it clearer that the LCA solution space is merely a sampled version of that of MVDR, hence can not be considered fully adaptive such as MVDR (although this, too, is heavily constrained).}
%
\qi{The use of non-SI units like cm is discouraged.}
\ai{We agree that non-SI units should be avoided, however had the belief that cm being a prefixed SI unit was valid? In the IEEE Styles Manual this unit is used several times as an example: 
\url{http://www.ieee.org/publications_standards/publications/journmag/online_style_manual-10292015.pdf} (e.g. on page 24 paragraph ``The En, Em, or Two-Em Dash'', and several times on page 25 paragraph ``Math'' bullet point 16). Will leave this as is for now pending any objections?}
%
\end{enumerate}

@@

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader --> The formulation in the Introduction might fit better "the incluence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" --> a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Another good point. This wording is now changed and a sentence elaborating on its meaning is added.}
%
\qi{"it was not clear how how many" --> delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" --> what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements on transmit. Changes made to reflect this.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer."--> real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. --> The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed it should, this paragraph is now rewritten.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" --> optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 --> could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture?
what exactly is the sectorscan mode?}
\ai{Thank you, we see that our formulation should be clarified. We are creating an image of the sector highlighted by a single ping of data (sectorscan), but are using data recorded by a synthetic aperture sonar (SAS). We mention it since SAS systems have a wide transmit beam intended to highlight multiple pings and thus does not produce the best sectorscan images.}
%
\end{enumerate}

>>>>

\begin{enumerate}
% \emph{General}
\hi{Introduction}
\qi{The authors show no evidence that bats use adaptive processing, remove this example.}
\ai{Very true. We have reworded the example to say that the bats have a sophisticated sonar instead. The term adaptive sonar is now only used on human made systems. We hope this change is satisfactory. }
%
\qi{It is not clear whether LCA is really an adaptive method that adapts weights on the fly or a method that a posteriori decides which window shows best results.}
\ai{We appreciate the remark. We are using a system level definition of adaptivity that includes any kind of dynamic and data dependent behavior, hence feel that both beamformers fall in that category. Both methods process the pixels in a data dependent manner, resulting in non linear image. We have tried to express it clearer that the LCA solution space is merely a sampled version of that of MVDR, hence can not be considered fully adaptive such as MVDR (although this, too, is heavily constrained).}
%
\qi{The use of non-SI units like cm is discouraged.}
\ai{We agree that non-SI units should be avoided, however had the belief that cm being a prefixed SI unit was valid? In the IEEE Styles Manual this unit is used several times as an example: 
\url{http://www.ieee.org/publications_standards/publications/journmag/online_style_manual-10292015.pdf} (e.g. on page 24 paragraph ``The En, Em, or Two-Em Dash'', and several times on page 25 paragraph ``Math'' bullet point 16). Will leave this as is for now pending any objections?}
%
\end{enumerate}

@@

\begin{enumerate}
% \emph{General}
\hi{Abstract}
\qi{"the array's spatial covariance matrix" might be a bit shocking for the non-expert Reader --> The formulation in the Introduction might fit better "the influence of noise ..."}
\ai{This is a good point. We have reformulated the sentence to speak of computing the spatial statistics instead.}
%
\hi{Page 2}
\qi{"6 of which were micro-steered" --> a short explanation or reference might help to understand what is meant by "micro-steered"}
\ai{Another good point. This wording is now changed and a sentence elaborating on its meaning is added.}
%
\qi{"it was not clear how how many" --> delete 1 x "how"}
\ai{Thank you. Corrected.}
%
\qi{"with an element beamwidth" --> what is meant by element beamwidth? Maybe an additional figure could be used to explain this.}
\ai{Good remark. We meant the -3dB opening angle of the elements on transmit. Changes made to reflect this.}
%
\hi{Page 3, after (1)}
\qi{"Applying a window that trails off .... Minimum variance distortion-less response (MVDR) beamformer."--> real and complex Windows? The introduction should be more formal: x ist introduced as delayed data, weights or delays to change, or both is explained later. --> The difference between noise and sidelobes should be pointed out.}
\ai{}
%
\hi{Page 5, equation (5)}
\qi{The lateral correlation and the reason why equation (5) is a good choice should be better explained.}
\ai{Indeed it should, this paragraph is now rewritten.}
%
\hi{Page 6, last row}
\qi{"they are optimal for any value" --> optimal in which sense?}
\ai{Thank you. This was mentioned earlier in the same paragraph, just after (8).}
%
\hi{Fig 3}
\qi{why is a 40x40 pixel group a good choice? could the associated broadside direction be made visible in the figure, too?}
\ai{This is an excellent question. This should perhaps be related to the detail level in the image, which in turn depends on the array's imaging performance.}
%
\hi{Page 8}
\qi{reference to Fig.1 --> could the sequence of figures be changes to have Fig. 1 closer to this paragraph}
\ai{Valid point. In our two column print the figure is on the page before its first reference. }
%
\hi{Page 11}
\qi{where is the synthetic aperture needed/applied in this work, or is it just the name of the array? how does the work on LCA/MVDR Change the Quality of synthetic aperture?
what exactly is the sectorscan mode?}
\ai{Thank you, we see that our formulation should be clarified. We are creating an image of the sector highlighted by a single ping of data (sectorscan), but are using data recorded by a synthetic aperture sonar (SAS). We mention it since SAS systems have a wide transmit beam intended to highlight multiple pings and thus does not produce the best sectorscan images.}
%
\end{enumerate}
